Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/appendix.tex
clarification

\newpage
\subsection{Feature importance}
\label{appendix:feature_importance}

>>>>

\newpage
\subsection{Modeling measurement noise}

Equation \ref{eq:model} does not explicitly contain a measurement noise term. Yet, in moast experimental cases, the problem is best described as:
\begin{equation}
  Y = (XE+N)F+M
  \label{eq:model_noisy_measure}
\end{equation}
  with $M\in \mathbb{R}^{n \times d_y}$.

This equation is actually equivalent to Equation \ref{eq:model} given our hypotheses. Indeed, we can rewrite $M = MF^{-1}F$ over $Img(F)$, which leads to:
$$Y = (XE+N)F+M = (XE+N+MF^{-1})F = (XE+N')F$$

Consequently, assuming that $F$ is full rank on $Img(XE)$, B2B yields the same solutions to equations \ref{eq:model} and \ref{model_noisy_measure}.

\subsection{Feature importance}
\label{appendix:feature_importance}

### 2019-11-13 paper/paper.tex
fix
clarification

We consider the measurement of multivariate signal $Y \in \mathbb{R}^{n \times d_y}$, generated from a set of putative causes $X \in \mathbb{R}^{n \times d_x}$, via some unknown linear apparatus $F \in \mathbb{R}^{d_x \times d_y}$.
%
Not all the variables in $X$ exert a causal influence on $Y$.
%
By considering a square binary diagonal matrix of \emph{causal influences} $E \in \mathbb{D}^{d_x \times d_x}$, we denote by $XE$ the causal factors of $Y$.
%
In summary, the problem can be formalized as:
%
\begin{equation}
    y_i = (x_i E + n_i) F
    \label{eq:model}
\end{equation}
%
where $i$ is a given sample, and $n$ is a centered, unobserved noise variable.
%
While the triplet of variables $X$ and $N$ are independent, we allow each of them to have any form of covariance.
% what is a general covariance matrix?
%
In practice, we observe $n$ samples $(X, Y)$ from the model.
%
This problem space, along with the sizes of all variables involved, is illustrated in Figure~\ref{fig:b2b}.
%
Given the model in Equation~\eqref{eq:model}, \textbf{the goal} of Back-to-Back Regression (B2B) is to estimate the matrix of causal influences $E$.

Note that the absence, in our model, of measurement noise over $Y$, is not restrictive. Starting from a model with measurement noise $M$, $$Y=(XE+N)F+M$$ On $Img(F)$,
we can rewrite $M = MF^{-1}F$, and we have
$$Y = (XE+N)F+M = (XE+N+MF^{-1})F = (XE+N')F$$
If $F$ has full rank, or in $Img(F)$, the two models are equivalent.

>>>>

We consider the measurement of multivariate signal $Y \in \mathbb{R}^{n \times d_y}$, generated from a set of putative causes $X \in \mathbb{R}^{n \times d_x}$, via some unknown linear apparatus $F \in \mathbb{R}^{d_x \times d_y}$.
%
Not all the variables in $X$ exert a causal influence on $Y$.
%
By considering a square binary diagonal matrix of \emph{causal influences} $E \in \mathbb{D}^{d_x \times d_x}$, we denote by $XE$ the causal factors of $Y$.
%
In summary, the problem can be formalized as:
%
\begin{equation}
    y_i = (x_i E + n_i) F
    \label{eq:model}
\end{equation}
%
where $i$ is a given sample, and $n_i$ is a sample-specific noise drawen from a centered distribution.
%
While the triplet of variables $X$ and $N$ are independent, we allow each of them to have any form of covariance.
% what is a general covariance matrix?
%
In practice, we observe $n$ samples $(X, Y)$ from the model.
%
This problem space, along with the sizes of all variables involved, is illustrated in Figure~\ref{fig:b2b}.
%
Given the model in Equation~\eqref{eq:model}, \textbf{the goal} of Back-to-Back Regression (B2B) is to estimate the matrix of causal influences $E$.
